Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-10-17 papers/thesis-kirstie/thesis.tex
more edits on intro

While models for particular fluids were being created, powerful methods to describe the properties 
of fluids in general were also being developed. In the late 1950s, Scaled Particle 
Theory (SPT)~\cite{ReissSPT} was introduced from which an equation of state, and
an expression for the excess Helmholtz free energy of a homogeneous Hard-Sphere fluid can be 
obtained~\cite{Hansen}. 
%Percus and Yevick took another approach to the Hard-Sphere fluid.
In 1961 Morita and Hiroike introduced a density functional approach~\cite{MoritaDFT} to finding the equilibrium grand free energy, 
or the equilibrium Helmholtz free energy in the case of a canonical ensemble, and the cooresponding equilibrium 
number density profile for inhomogeneous fluids. To use this approach, a functional must be 
constructed for a particular fluid.
%DFT Evans 1979
In 1989 Rosenfeld introduced Fundamental Measure Theory (FMT)~\cite{rosenfeld1989} 
to construct a functional for 
%which provides an expression for the excess Helmholtz free energy of an inhomogeneous 
the Hard-Sphere fluid. 
Tarazona later improved on the method by introducing a tensor version of the 
functional~\cite{tarazonaphi3}, and in 1999 Schmidt adopted FMT for soft spheres 
forming Soft Fundamental Measure Theory (SFMT)\cite{schmidt1999density}.

In this paper, Density Functional Theory (DFT) will be used to predict the freezing of a 
Weeks-Chandler-Anderson model fluid by applying SFMT with Schmidt's proposed 
erf model\cite{schmidt2000fluid} to form the functional. %for generating the weight funcions, 
%and Tarazona's tensor functional. 
Results will be compared to those generated from Monte-Carlo simulations.
%\[{}\]
\newline
\newline
\noindent IIA. Model Fluids and the Weeks-Chandler-Anderson Fluid (WCA)

>>>>

While models for particular fluids were being created, powerful methods to describe the properties 
of fluids in general were also being developed. In the late 1950s, Scaled Particle 
Theory (SPT)~\cite{ReissSPT} was introduced from which an equation of state, and
an expression for the excess Helmholtz free energy of a homogeneous Hard-Sphere fluid can be 
obtained~\cite{Hansen}. \color{red}ADD Percus-Yevick introduced an alternative method...OZ... \color{black}
%Percus and Yevick took another approach to the Hard-Sphere fluid.
Led by the consistency bewteen results from SPT and Percus-Yevick, in 1961 Morita and Hiroike 
introduced a density functional approach~\cite{MoritaDFT} to finding the equilibrium grand free energy 
(the equilibrium Helmholtz free energy in the case of a canonical ensemble), and the cooresponding equilibrium 
number density profile for inhomogeneous fluids. To use this approach, a functional must be 
constructed for a particular fluid.
%DFT Evans 1979
In 1989 Rosenfeld introduced Fundamental Measure Theory (FMT)~\cite{rosenfeld1989} 
(which can be constructed from SPT~\cite{santos2012phi3}) to form a functional for 
%which provides an expression for the excess Helmholtz free energy of an inhomogeneous 
the Hard-Sphere fluid. 
Tarazona later improved on the method by introducing a tensor version of the 
functional~\cite{tarazonaphi3}, and in 1999 Schmidt adopted FMT for soft spheres 
forming Soft Fundamental Measure Theory (SFMT)\cite{schmidt1999density}.

Schmidt applied his Soft Fundamental Measure Theory to various fluids with soft repulsive 
and soft attractive potentials, and developed an erf model for 
spheres with a steep, short-range soft repulsive potential~\cite{schmidt2000fluid}. In this paper, 
Density Functional Theory (DFT) will be used to predict the freezing of a 
Weeks-Chandler-Anderson model fluid by applying SFMT with Schmidt's proposed 
erf model to form the functional for the excess Helmholtz free energy. 
%for generating the weight funcions, and Tarazona's tensor functional. 
Results will be compared to those generated from Monte-Carlo simulations.
%\[{}\]
\newline
\newline
\noindent IIA. Model Fluids and the Weeks-Chandler-Anderson Fluid (WCA)
